Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Add modification to previous commit.

\caption{HRP-2 grabs a ball on a shelf, puts it on another shelf, and comes back to 
  a rest position. Static balance constraints are enforced along the path, and 
  the intermediary goals consisting in grasping and displacing the ball are defined
  implicitly as inverse kinematics tasks.}
\label{fig:wb-shelves}
\end{figure}

>>>>

\caption{HRP-2 grabs a ball on a shelf, puts it on another shelf, and comes back to 
  a rest position. Static balance constraints are enforced along the path, and 
  the intermediary goals consisting in grasping and displacing the ball are defined
  implicitly as inverse kinematics constraints.}
\label{fig:wb-shelves}
\end{figure}
